---
title: "Data Cleaning"
author: "Chelsea Harmon"
date: "1/27/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(broom)
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = T, cache = F, tidy = F, warning = F, message = F)  # Code not shown by default

# Set global ggplot theme
theme_set(theme_bw() + theme(panel.grid = element_blank(),
                             strip.text = element_blank(),
                             strip.background = element_blank(),
                             legend.position = "none"))
```

#Getting Data From data Folder output from Psychopy 

```{r,include=FALSE}

all.file.names <- list.files(path = "/Users/chelseaharmon/Dropbox/danlab/Tasks/motorSequenceLearning/sequenceLearning/data/V1W1", pattern = ".csv")
length(all.file.names)
#all.file.names
#517 files 

#write.table(all.file.names, file = "all.file.namesV1W1_11.17.21.txt", quote = F, row.names = F, col.names = F, sep = ",")

all.file.path.names <- 1:length(all.file.names)
for(i in 1:length(all.file.names)){all.file.path.names[i] <- paste("/Users/chelseaharmon/Dropbox/danlab/Tasks/motorSequenceLearning/sequenceLearning/data/V1W1/",all.file.names[i], sep='')
}

#write.table(all.file.path.names, file = "all.file.pathsV1W1_11.17.21.txt", quote = F, row.names = F, col.names = F, sep = ",")

data.list.all <- list()
length(all.file.path.names)


for(i in 1:length(all.file.path.names)){
# assign data frame for each csv file and save it in the list of dataframes.
data.list.all[[i]] <- data.frame(read.csv(all.file.path.names[i], stringsAsFactors=T))
}

all.subject.list <- substr(all.file.names, start=1, stop=5)


#finding the biggest file output 
finding.longest.file <- data.frame(1:length(data.list.all))
for(i in 1:length(data.list.all)){
  finding.longest.file[i, 1] <- (all.subject.list[i])
  finding.longest.file[i, 2] <- (all.file.names[i])
  finding.longest.file[i, 3] <- (length(data.list.all[[i]]$participant))}


finding.longest.file <- 
  finding.longest.file[
  order(finding.longest.file[,1], -finding.longest.file[,3]),
]

use.these.data.files <- finding.longest.file[!duplicated(finding.longest.file$X1.length.data.list.),2]
W1.subject.list <- substr(use.these.data.files, start=1, stop=5)
length(W1.subject.list)
#(W1.subject.list)
#242

W1.use.these.data.files <- use.these.data.files

#write.table(W1.use.these.data.files, file = "file.namesV1W1_11.16.21.txt", quote = F, row.names = F, col.names = F, sep = ",")


W1.file.path.names <- 1:length(W1.use.these.data.files)
W1.file.path.names

for(i in 1:length(W1.use.these.data.files)){W1.file.path.names[i] <- paste("/Users/chelseaharmon/Dropbox/danlab/Tasks/motorSequenceLearning/sequenceLearning/data/V1W1/",use.these.data.files[i], sep='')
}

length(W1.file.path.names)

#write.table(W1.file.path.names, file = "file.pathsV1W1_11.17.21.txt", quote = F, row.names = F, col.names = F, sep = ",")

```

#Grabbing Wave 2 data 
```{r,include=FALSE}

W2.all.file.names <- list.files(path = "/Users/chelseaharmon/Dropbox/danlab/Tasks/motorSequenceLearning/sequenceLearning/data/V2W2", pattern = ".csv")
length(W2.all.file.names)
#101

#write.table(all.file.names, file = "all.file.namesV2W2_11.17.21.txt", quote = F, row.names = F, col.names = F, sep = ",")

W2.all.file.path.names <- 1:length(W2.all.file.names)
for(i in 1:length(W2.all.file.names)){W2.all.file.path.names[i] <- paste("/Users/chelseaharmon/Dropbox/danlab/Tasks/motorSequenceLearning/sequenceLearning/data/V2W2/",W2.all.file.names[i], sep='')
}

#write.table(all.file.path.names, file = "all.file.pathsV2W2_05.17.20.txt", quote = F, row.names = F, col.names = F, sep = ",")

W2.data.list.all <- list()

for(i in 1:length(W2.all.file.path.names)){
# assign data frame for each csv file and save it in the list of dataframes.
W2.data.list.all[[i]] <- data.frame(read.csv(W2.all.file.path.names[i], stringsAsFactors=T))
}

W2.all.subject.list <- substr(W2.all.file.names, start=1, stop=5)
length(W2.all.subject.list)

#finding the biggest file output 
W2.finding.longest.file <- data.frame(1:length(W2.data.list.all))
for(i in 1:length(W2.data.list.all)){
  W2.finding.longest.file[i, 1] <- (W2.all.subject.list[i])
  W2.finding.longest.file[i, 2] <- (W2.all.file.names[i])
  W2.finding.longest.file[i, 3] <- (length(W2.data.list.all[[i]]$participant))}


W2.finding.longest.file <- 
  W2.finding.longest.file[
  order(W2.finding.longest.file[,1], -W2.finding.longest.file[,3]),
]
head(W2.finding.longest.file)
W2.use.these.data.files <- W2.finding.longest.file[!duplicated(W2.finding.longest.file$X1.length.W2.data.list.),2]
#View(finding.longest.file)
W2.subject.list <- substr(W2.use.these.data.files, start=1, stop=5)
W2.subject.list
#W2.use.these.data.files
length(W2.subject.list)
#48

#write.table(W2.use.these.data.files, file = "file.namesV2W2_11.17.21.txt", quote = F, row.names = F, col.names = F, sep = ",")


W2.file.path.names <- 1:length(W2.use.these.data.files)
for(i in 1:length(W2.use.these.data.files)){W2.file.path.names[i] <- paste("/Users/chelseaharmon/Dropbox/danlab/Tasks/motorSequenceLearning/sequenceLearning/data/V2W2/",W2.use.these.data.files[i], sep='')
}
length(W2.file.path.names)

#write.table(W2.file.path.names, file = "file.pathsV2W2_11.16.21.txt", quote = F, row.names = F, col.names = F, sep = ",")
```


#Making sepearte csv with demographcis or W1 and W2 
```{r}
#wave 1
length(W1.file.path.names)
#242
taskData <- read.csv((W1.file.path.names[1]), stringsAsFactors = F)

W1.file.path.names <- W1.file.path.names[-1]
W1.use.these.data.files <- W1.use.these.data.files[-1]


for(i in 1:length(W1.file.path.names)){
  subData <- read.csv(W1.file.path.names[i])
  taskData <- plyr::rbind.fill(taskData, subData)
}


(unique(taskData$participant))



#renaming subjects who were mis-entered 
taskData$participant[taskData$participant=="PA101"] <- 101
taskData$participant[taskData$participant=="PA246"] <- 246
taskData$participant[taskData$participant=="PA325"] <- 325
taskData$participant[taskData$participant=="PA326"] <- 326
taskData$participant[taskData$participant=="PA246"] <- 246
#taskData$participant[taskData$participant=="PA008"] <- 8
#taskData$participant[taskData$participant=="PA010_V2W2"] <- 10
#taskData$participant[taskData$participant=="PA025"] <- 25
#taskData$participant[taskData$participant=="pa034"] <- 34
#taskData$participant[taskData$participant=="PA070_V2W2"] <- 70

write.csv(taskData, file= "Wave1RawData_12.03.21.csv", row.names = F)

```

#Making csv with all subjects data

```{r, include=FALSE}
#Because thius was run aleady we can load the data at the bottom of this code chunk 
#
# #taskData1 <- read.csv((file.path.names[1]), stringsAsFactors = F)
# 
# #file.path.names[1]
# #taskData <- read.csv((file.path.names[1]), stringsAsFactors = F)
# all.use.these.data.files <- c(W1.use.these.data.files,W2.use.these.data.files)
# 
# #write.table(all.use.these.data.files, file = "all.file.names_11.16.21.txt", quote = F, row.names = F, col.names = F, sep = ",")
# (all.use.these.data.files)
# length(W1.use.these.data.files) 
# length(W2.use.these.data.files)
# 
# 242+48
# 
# both.waves.file.path.name <- c(W1.file.path.names, W2.file.path.names)
# #write.table(both.waves.file.path.name, file = "all.file.paths_11.16.21.txt", quote = F, row.names = F, col.names = F, sep = ",")
# 
# length(both.waves.file.path.name)
# 
# #write.table(both.waves.file.path.name, file = "both.waves.file.paths_11.16.21.txt", quote = F, row.names = F, col.names = F, sep = ",")
# 
# taskData <- read.csv((both.waves.file.path.name[1]), stringsAsFactors = F)
# 
# both.waves.file.path.name <- both.waves.file.path.name[-1]
# all.use.these.data.files <- all.use.these.data.files[-1]
# 
# 
# #dirTask <- "/Users/chelseaharmon/Dropbox/danlab/Tasks/motorSequenceLearning/sequenceLearning/data/V1W1/"
# #use.these.data.files <- use.these.data.files[-1]
# all.use.these.data.files
# both.waves.file.path.name
# 
# 
# for(i in 1:length(both.waves.file.path.name)){
#   subData <- read.csv(both.waves.file.path.name[i])
#   taskData <- plyr::rbind.fill(taskData, subData)
# }
# 
# 
# length(taskData)
# length(unique(taskData$participant))
# (unique(taskData$participant))
# (length(unique(taskData$participant)))
# 
#
##Renaming strangely named participants 
# taskData$participant[taskData$participant=="PA101"] <- 101
# taskData$participant[taskData$participant=="PA246"] <- 246
# taskData$participant[taskData$participant=="PA325"] <- 325
# taskData$participant[taskData$participant=="PA326"] <- 326
# taskData$participant[taskData$participant=="PA246"] <- 246
# taskData$participant[taskData$participant=="PA008"] <- 008
# taskData$participant[taskData$participant=="PA010_V2W2"] <- 010
# taskData$participant[taskData$participant=="PA025"] <- 025
# taskData$participant[taskData$participant=="pa034"] <- 034
# taskData$participant[taskData$participant=="PA070_V2W2"] <- 070
# 
# #repeated data PA006 PA031 PA058 PA059 PA060 PA061 PA069
# 
# names(taskData)

#write.csv(taskData, file= "all.subject.task.data_11.16.21.csv", row.names = F)
taskData <- read.csv("all.subject.task.data_11.16.21.csv")
length(unique(taskData$participant))

count(taskData$participant)

#View(taskData)
#IMPORTANT: Demographic data should be merged with subject data AFTER separating into block - In this script we seperate pre and post touch screen data into blocks - look at SequenceFixingDemographicsAndModelsCorrectBlock1.19.2022.Rmd for next step of adding demographics - 
```


#Seperatng touch screen 
```{r}
#View(taskData[taskData$allowableKey=="['num_7', 'num_4', 'num_1', 'num_0']",])
#taskData$preTouchScreen <- ifelse(taskData$allowableKey=="['num_7', 'num_4', 'num_1', 'num_0']", 1, 0)
#taskData$expName

#unique(taskData$preTouchScreen)
#table(taskData$preTouchScreen, taskData$allowableKey)

#taskData$preTouchScreen <- 1
#taskData$preTouchScreen[is.na(taskData$correctLocation)] <- 1
#taskData$preTouchScreen[!is.na(taskData$correctLocation)] <- 0

#Filter out non usable data 
#Those that were run with incorrect order (sequence, random, random, sequence)
#PA098 PA127 PA136 PA086
#View(taskData)

taskData <- taskData[!taskData$participant=="98",]
taskData <- taskData[!taskData$participant=="127",]
taskData <- taskData[!taskData$participant=="136",]
taskData <- taskData[!taskData$participant=="86",]


length(unique(taskData$participant))


#Task Data Touch Screen seperate data frame - possibly save this for later 
#taskDataTouch <- taskData[complete.cases(taskData$correctLocation), ]
#taskDataTouchCheck <- taskData[taskData$preTouchScreen ==1,]

#unique(taskDataTouch$participant)
#unique(taskDataTouchCheck$participant)

unique(taskData$date)
taskData$date1 <- substr(taskData$date, start=1, stop=11)
taskData$date1 
taskData$date1 <- as.Date(taskData$date1, format = ("%Y_%b_%d"))
class(taskData$date1)

taskData$PreTouchByDate<- ifelse(taskData$date1 > "2018-06-12", 0, 1)
unique(taskData$participant)

unique(taskData$participant[taskData$PreTouchByDate==1])
unique(taskData$participant[taskData$PreTouchByDate==0])
length(unique(taskData$participant[taskData$PreTouchByDate==1]))
length(unique(taskData$participant[taskData$PreTouchByDate==0]))

taskDataTouch <- taskData[taskData$PreTouchByDate==1,]
taskData <- taskData[taskData$PreTouchByDate==0,]

(unique(taskDataTouch$participant))
length(unique(taskData$participant))
head(taskDataTouch)

#write.csv(taskData, file= "post_touchscreen.task.data_11.16.21.csv", row.names = F)
#write.csv(taskDataTouch, file= "pre_touchscreen.task.data_11.16.21.csv", row.names = F)

```


#Cleaning touch screen data 
```{r}

#head(taskDataTouch)
#names(taskDataTouch)

#Making new file with quesitons 
#questionsResponsesTouch <- taskDataTouch[!complete.cases(taskDataTouch$stimulusPresent.t), ]
#taskDataTouch <- taskDataTouch[complete.cases(taskDataTouch$stimulusPresent.t), ]

#taskDataTouch$keyResponse <- as.character(taskDataTouch$key_resp_9.keys)
#taskDataTouch$keyResponseTimes <- as.character(taskDataTouch$key_resp_9.rt)

#unique(taskDataTouch)

#Touch screen columns 
#taskDataTouch <- subset(taskDataTouch, select=c('participant', 'date', 'stimulusPresent.t', 'responseTimeCorrect', 'responseTimeIncorrect', 'trialIncorrect', 'correctLocation', 'pressLoc', 'anticipatoryResponse', 'preTouchScreen')) #


#table(taskData$participant, taskData$correctLocation)
#table(taskData$participant, taskData$preTouchScreen)
#table(taskData$participant, taskData$preTouchScreen)

#unique(taskDataTouch$participant)
#unique(taskData$date)
#taskDataDateSep <- separate(data = taskData, col = date, into = c("Year", "Month", "Day", "Time"), sep = "\\_")
#taskDataDateSep$Year
#unique(taskDataAll$preTouchScreen)


#taskData$trialIncorrect[is.na(taskData$trialIncorrect)] <- 0
#taskData$anticipatoryResponse[is.na(taskData$anticipatoryResponse)] <- 0

#taskData$trialCorrect <- taskData$trialIncorrect + 1
#taskData$trialCorrect[taskData$trialCorrect==2] <- 0

```


#Cleaning pre touch screen data 

```{r}
taskDataPreTouch <- read.csv("pre_touchscreen.task.data_11.16.21.csv")

(unique(taskDataPreTouch$repetitionNumber))



(unique(taskDataPreTouch$repeitionNumber))
#View(taskDataPreTouch)
unique(taskDataPreTouch$thisRepN)
#Pre Touch screen columns 

#Seperating out questionnaire data 
unique(taskDataPreTouch$trials_questions.thisRepN)
#taskDataPreTouch[taskDataPreTouch$trials_questions.thisRepN==0,]


questionnaireDataPreTouch<- taskDataPreTouch %>% 
  filter(taskDataPreTouch$trials_questions.thisRepN==0) %>% 
  subset(select=c('participant', 'date1', 'stimulusPresent.t', 'correctKey', 'keyRespCorrect', 'correctKeyPressNum', 'key_resp_9.rt', 'key_resp_9.keys', 'trialCorrect', 'repetitionNumber', 'anticipatoryResponse', 'PreTouchByDate', 'recallResponse', 'recallResponseTime', 'RecordAnswer.rt', 'RecordAnswer.keys', 'questionsResponses')) 


taskDataPreTouch <- taskDataPreTouch %>% 
  filter(taskDataPreTouch$stimulusPresent.t>0) %>% 
  subset(select=c('participant', 'date1', 'stimulusPresent.t', 'correctKey', 'keyRespCorrect', 'correctKeyPressNum', 'key_resp_9.rt', 'key_resp_9.keys', 'trialCorrect', 'repetitionNumber', 'anticipatoryResponse', 'PreTouchByDate')) #

write.csv(questionnaireDataPreTouch, "questionnaireDataPretTouchCleaned1.28.2022.csv", row.names=F)


```

#seperating data into blocks, pre touch screen 

```{r}

unique(taskDataPreTouch$participant)[2]


length(unique(taskDataPreTouch$participant))

table(taskDataPreTouch$participant)

#for(i in 1:length(unique(taskDataPreTouch$participant))){
#  taskDataPreTouch$TrialNum <- 
#  taskDataPreTouch[taskDataPreTouch$participant==unique(taskDataPreTouch$participant)[2],]

#}


taskDataPreTouch$TrialNum <- sequence(rle(taskDataPreTouch$participant)$lengths)



#excluding incomplete data, excluding subjects 58 (for 2 blocks), 60 (for 1 block), 73 (for 1 block), 80 (for 2 blocks), 82 (for not completing 1 full block), 84 (for 1 block), 93 (for not completing block 3) = 7 subjects 
taskDataPreTouch$participant

taskDataPreTouch <- taskDataPreTouch %>% 
  filter(!participant %in% c(58, 60, 73, 80, 82, 84, 93))

#in group analyses is it okay to keep those who did not complete the task, or should we only complete full data? - ask Paul, statistical question 


unique(taskDataPreTouch$participant)
length(unique(taskDataPreTouch$participant))
unique(taskData$participant)

#repeated in pre and post touch screen - 6, 



```


#seperating pre touch screen into Blocks 
```{r}

taskDataPreTouchBlocks1 <- taskDataPreTouch 
#taskDataPreTouchBlocks1$Group <-  taskDataPreTouchBlocks1$Trial

#Post Touch screen has sequence length 8 for 10 sequences per block 
taskDataPreTouchBlocks1$Group1 <- taskDataPreTouchBlocks1$TrialNum <= 80 #100 
taskDataPreTouchBlocks1$Group2 <- between(taskDataPreTouchBlocks1$Trial, 81, 160)  #101,  200 ) 
taskDataPreTouchBlocks1$Group3 <- between(taskDataPreTouchBlocks1$Trial, 161, 240) #201,  300 ) 
taskDataPreTouchBlocks1$Group4 <- between(taskDataPreTouchBlocks1$Trial, 241, 320)   #301,  400 ) 

taskDataPreTouchBlocks1$Group[taskDataPreTouchBlocks1$Group1 == TRUE] <- "Block1"
taskDataPreTouchBlocks1$Group[taskDataPreTouchBlocks1$Group2 == TRUE] <- "Block2"
taskDataPreTouchBlocks1$Group[taskDataPreTouchBlocks1$Group3 == TRUE] <- "Block3"
taskDataPreTouchBlocks1$Group[taskDataPreTouchBlocks1$Group4 == TRUE] <- "Block4"
Group <- taskDataPreTouchBlocks1$Group

taskDataPreTouch <- (cbind(taskDataPreTouch, Group))
head(taskDataPreTouch)
unique(taskDataPreTouch$Group)
names(taskDataPreTouch)

write.csv(taskDataPreTouch, "dataPreTouchCleaned1.28.2022.csv", row.names=F)
#write.csv(taskDataPreTouch, "dataPreTouchCleaned1.19.2022.csv", row.names=F)

table(taskDataPreTouch$participant, taskDataPreTouch$Group)

#What are anticipatory responses that are incorrect??? 

```



#Cleaning post touch screen data 
```{r, include=FALSE}
taskData <- read.csv("post_touchscreen.task.data_11.16.21.csv")
head(taskData)

#Seperating out questionnaire data 
names(taskData)
#View(taskData)
unique(taskData$stimulusPresent.t)
unique(taskData$X)

#Check these - are they real pre touch data snuck into the post touch data.frame?
taskData[taskData$correctKey=="['num_4']",]


#questionnaireDataTouch<- taskData %>% 
#  filter(taskData$trials_questions.thisRepN==0) %>% 
#  subset(select=c('participant', 'date1', 'stimulusPresent.t', 'correctKey', 'keyRespCorrect', 'correctKeyPressNum', 'key_resp_9.rt', 'key_resp_9.keys', 'trialCorrect', #'repetitionNumber', 'anticipatoryResponse', 'PreTouchByDate', 'recallResponse', 'recallResponseTime', 'RecordAnswer.rt', 'RecordAnswer.keys', 'questionsResponses')) 

#Check question respones and RecordAnswer.keys - checking for if questoinnresponses are pre touchscreen data only (should not be in this data set)
questionnaireDataTouch<- taskData %>% 
  filter(taskData$trials_questions.thisRepN==0) %>% 
  subset(select=c('participant', 'date1', 'stimulusPresent.t', 'correctKey', 'keyRespCorrect', 'correctKeyPressNum', 'key_resp_9.rt', 'key_resp_9.keys', 'trialCorrect', 'repetitionNumber', 'anticipatoryResponse', 'PreTouchByDate', 'recallResponse', 'recallResponseTime', 'RecordAnswer.keys' ,'questionsResponses', 'trials_questions.thisRepN', 'trials_questions.thisTrialN', 'trials_questions.thisN',  'trials_test.thisRepN', 'trials_test.thisTrialN','trials_test.thisN', 'trials_test.thisIndex', 'trials_recogtest.thisRepN', 'trials_recogtest.thisTrialN', 'trials_recogtest.thisN', 'trials_recogtest.thisIndex', 'AnswerFinished.keys', 'AnswerFinished.rt','RecordAnswer.keys')) #' trials_questions.thisIndex')) 

#I don't think I care abou tthis so leave it out - RecordAnswer.rt - this is the time for each letter press for the open ended question - do you play an instrument 

#taskData <- taskData %>% 
#  filter(taskData$stimulusPresent.t>0) %>% 
#  subset(select=c('participant', 'date1', 'stimulusPresent.t', 'correctKey', 'keyRespCorrect', 'correctKeyPressNum', 'key_resp_9.rt', 'key_resp_9.keys', 'trialCorrect', #'repetitionNumber', 'anticipatoryResponse', 'PreTouchByDate')) #

taskData <- taskData %>% 
  filter(taskData$stimulusPresent.t>0) %>% 
  subset(select=c('participant', 'date1', 'stimulusPresent.t', 'correctKey', 'correctKeyPressNum', 'trials_3.thisTrialN','trials_3.thisIndex', 'trials_2.thisRepN', 'trials_2.thisTrialN', 'correctLocation', 'correctImage', 'trialCorrect', 'trials_2.thisN', 'trials_2.thisIndex',  'repetitionNumber', 'anticipatoryResponse', 'responseTimeCorrect', 'responseTimeIncorrect', 'pressLoc', 'trialIncorrect', 'session', 'correctKey.1', 'frameRate', 'PreTouchByDate')) #

#View(taskData)
unique(taskData$participant)

#These are post touch screen answers 
#taskData <- taskData %>% select(-c('responseTimeCorrect', 'responseTimeIncorrect', 'trialIncorrect', 'correctLocation', 'pressLoc', 'anticipatoryResponse', 'correctImage'))

subject75data <- taskData[(taskData$participant==75),]
#View(subject75data)
length(subject75data$repetitionNumber)

subject6data <- taskData[(taskData$participant==6),]
length(subject75data$repetitionNumber)

subject31data <- taskData[(taskData$participant==31),]
length(subject75data$repetitionNumber)

#table(taskData$participant, taskData$pawPatrol1) >337
#table(taskData$participant, taskData$pawPatrol1) 

#incomplete data subject numbers 45, 112, 236, 253, 259, 274, 311, 317 ??????????????????????????
#subjects who completed post touch screen twice 3, 31


write.csv(questionnaireDataTouch, "questionnaireDataPostTouchCleaned1.28.2022.csv", row.names=F)

```


#seperating data into Blocks 
```{r}

taskData$repetitionNumber


taskData$TrialNum <- sequence(rle(taskData$participant)$lengths)

unique(taskData$TrialNum)


# taskDataNoOutliers <- taskData[taskData$responseTimeCorrect < 100,]
# 
# ggplot(data=taskDataNoOutliers, aes(TrialNum, responseTimeCorrect, group=participant, color=participant)) + 
#   geom_point() + 
#   geom_line()
# 
# summaryAllValues <- taskData %>% 
#   group_by(participant, Group) %>%
#   summarise_at(vars(trialCorrect), funs(mean(., na.rm=TRUE), sd(., na.rm=T),se=sd/sqrt(n())))
# 
# 337/4
# taskData$Block <-rep(1:8, length=nrow(x))
# 
# library(dplyr)
# taskData %>% 
#  group_by(participant) %>% 
#  mutate(Block= c(rep(1:8)))
# 
# 
# taskData %>% 
#   group_by(participant) %>% 
#   mutate(num_in_group=seq_along(repetitionNumber)) %>% 
#   as.data.frame
# 
# df %>%
#  group_by(cat) %>%
#  mutate(num = 1:n())
# taskDataBlocks1 <- ddply(taskData, .(participant), mutate, Trial = seq_along(repetitionNumber))


#taskData$Trial <- c(1:length(taskData$repetitionNumber))
#taskDataBlocks1 <- ddply(taskData, .(participant), mutate, Trial = seq_along(repetitionNumber))
taskDataBlocks1 <- taskData
#taskDataBlocks1$Group <-  taskDataBlocks1$Trial

#Post Touch screen has sequence length 8 for 10 sequences per block 
taskDataBlocks1$Group1 <- taskDataBlocks1$TrialNum <= 80 #100
taskDataBlocks1$Group2 <- between(taskDataBlocks1$Trial, 81, 160)  #101,  200 ) 
taskDataBlocks1$Group3 <- between(taskDataBlocks1$Trial, 161, 240) #201,  300 ) 
taskDataBlocks1$Group4 <- between(taskDataBlocks1$Trial, 241, 320)   #301,  400 ) 

taskDataBlocks1$Group[taskDataBlocks1$Group1 == TRUE] <- "Block1"
taskDataBlocks1$Group[taskDataBlocks1$Group2 == TRUE] <- "Block2"
taskDataBlocks1$Group[taskDataBlocks1$Group3 == TRUE] <- "Block3"
taskDataBlocks1$Group[taskDataBlocks1$Group4 == TRUE] <- "Block4"
Group <- taskDataBlocks1$Group

taskData <- (cbind(taskData, Group))
head(taskData)
unique(taskData$Group)
names(taskData)
length(unique(taskData$participant))

unique(taskData$participant)


write.csv(taskData, "dataPostTouchCleaned1.28.2022.csv", row.names=F)

#write.csv(taskData, "dataPostTouchCleaned1.15.2019.csv", row.names=F)



table(taskData$participant, taskData$Group)

#What are anticipatory responses that are incorrect??? 
```




#Removing data for incomplete or repeated 
```{r}
#Removing incomplete data 
taskData <- taskData[!taskData$participant=='112',] #2 blocks only 
taskData <- taskData[!taskData$participant=='253',] #has only 1 block
taskData <- taskData[!taskData$participant=='311',] #only 2 blocks
taskData <- taskData[!taskData$participant=='317',] #only did a few trials of block 1 

#Repeated subject pre and post touch screen == 6 
#Repeated subject post touch screen twice == 3, 31

taskData <- taskData[!taskData$participant=='6',] #just use pre touch screen data so remove from post touch screen data sheet 

unique(taskData[taskData$participant=='3',]$date) #on elvis has two dates of data April 21 2019 and June 27 2019 - V2W2 - dates close together - check data entry master to see when this subject came in 

#View(taskData[taskData$participant=='3',]) 
unique(taskData[taskData$participant=='31',]$date)

unique(taskData[taskData$participant=='33',]$date)
#View(taskData[taskData$participant=='33',])

names(taskData)

taskData %>% filter(participant=="3") %>%
  group_by(TrialNum) %>%
  summarise_at(vars(responseTimeCorrect),funs(mean(., na.rm=TRUE)))


taskDataSubj3 <- 
  taskData %>% filter(participant=="3")

taskDataSubj3
unique(taskDataSubj3$session)


taskDataSubj3$trialnumall <- 1:640
taskDataSubj3[1:320,]$trialnumall <- 0
taskDataSubj3[321:640,]$trialnumall <- 1
taskDataSubj3 %>% 
  group_by(trialnumall, Group) %>%
  summarise_at(vars(responseTimeCorrect),funs(mean(., na.rm=TRUE)))

#data was repeated 2x (they are the same) because there was an extra data collected o6/27/2019 where no data was actually collected. Here I am going to remove the repeated trials 321-640

taskDataSubj3 <- taskDataSubj3[taskDataSubj3$trialnumall==0,]
length(taskDataSubj3)
taskData <- taskData[!taskData$participant=='3',] 


taskDataSubj3 <- taskDataSubj3[,1:26]


table(taskData$participant, taskData$Group)

#Removing the repeated data for subject 31 
taskData %>% filter(participant=="31") %>%
  group_by(date1, Group) %>%
  summarise_at(vars(responseTimeCorrect),funs(mean(., na.rm=TRUE)))


taskData[taskData$participant==31,]$date1=="2019-06-07"

unique(taskData[taskData$date1=="2019-06-07",]$participant)

taskData<- taskData[!taskData$date1=="2019-06-07",] 

table(taskData$participant, taskData$Group)

taskData <- dplyr::rename(taskData, Block = Group)

write.csv(taskData, "dataPostTouchCleaned1.28.2022.csv", row.names=F)

table(taskDataPreTouch$participant, taskDataPreTouch$Group)
taskDataPreTouch <- dplyr::rename(taskDataPreTouch, Block = Group)

write.csv(taskDataPreTouch, "dataPreTouchCleaned1.28.2022.csv", row.names=F)


```




#Merging pre and post touch data 

```{r}
taskData
taskDataPreTouch

unique(taskData$participant)
unique(taskDataPreTouch$participant)

```



